Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-06 docs/evol.tex
improved table 6 layout
additional bug counter and diffs discussion

@@

\begin{landscape}
  \begin{table}
    \caption{Bug Persistence Comparison}
    \label{tbl:bug_persistence}
    \input{bug_persistence.tex}
    \small The matrix presents pairwise Mann-Whitney $U$ test results
    between the different bug categories. Each cell contains the test
    result (the value of $U$), the $p$-value, the average for each
    category and the sample size for each category. Cells in brackets show
    pairs where no statistically significant difference was found.
  \end{table}
\end{landscape}

>>>>

Although there seems to be zero tendency taken over all versions of
all projects together, the situation might be different in individual
projects. We therefore performed Spearman correlations between bug
counts and version ordinals in all projects we examined. These paint a
different picture from the above table, shown in
Figure~\ref{fig:bugsversioncorr}. The spike in point zero is explained
by the large number of projects for which no correlation could be
established---note that the scale is logarithmic.

But we can see that there were projects where a correlation could be
established, either positive or negative. The {\it Security High}
category is particularly bimodal, but this is explained by the small
number of correlations that could be established, nine in total. Taken
together with Table~\ref{tbl:bugsperversion} this suggests that: we
cannot say that across projects defect counts increase or decrease
significantly across time. But in individual projects, defect counts
can have a strong upwards or downwards tendency. There may be no such
thing as a ``project'' in general, only particular projects with their
own idiosyncrasies, quality features, and coding practices.

\begin{figure*}
  \centering
  \includegraphics[scale=0.4]{bugsversionscorr.pdf}
  \caption{Histograms of correlations between bug counts and version
    ordinals per project}
  \label{fig:bugsversionscorr}
\end{figure*}

@@

\begin{landscape}
  \begin{table}
    \setlength{\extrarowheight}{0.10cm}
    \caption{Bug Persistence Comparison}
    \label{tbl:bug_persistence}
    \resizebox{0.95\columnwidth}{!}{
    \input{bug_persistence.tex}}\\
    The matrix presents pairwise Mann-Whitney $U$ test results
    between the different bug categories. Each cell contains the test
    result (the value of $U$), the $p$-value, the average for each
    category and the sample size for each category. Cells in brackets show
    pairs where no statistically significant difference was found.
  \end{table}
\end{landscape}
